### 2018-07-06 docs/intro.tex
VERSION 0.8.0

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  intro.tex
%
%  Contains introduction and quick start for users.
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  (c) 2016-2017 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Under the auspices of the CCPs (Collaborative Computational Projects),
and in particular CCP5, we have a CCPForge project account at
\texttt{http://ccpforge.cse.rl.ac.uk/}
which provides revision control via SVN, issue tracking, and so on.

\paragraph{Users:}

Code releases may be downloaded via anonymous download
\begin{lstlisting}[style=terminalverbatim]
http://ccpforge.cse.rl.ac.uk/gf/project/ludwig/frs/
\end{lstlisting}
The current release is available as \texttt{ludwig-0.6.0.tar.gz}.
Alternatively, registered users can obtain the code via svn checkout
in the same way as developers.

\paragraph{Developers:}

Developers need to create an account at CCPForge, and let one of the
project owners\footnote{Currently: \texttt{kevin@epcc.ed.ac.uk},
\texttt{ohenrich@epcc.ed.ac.uk}}
know the user name so you can be added to the access list.

To download the entire code, developers need
\begin{lstlisting}
svn checkout --username <user> http://ccpforge.cse.rl.ac.uk/svn/ludwig
\end{lstlisting}
where \texttt{<user>} is replaced by your CCPForge user name. You will
see
\begin{lstlisting}
$ ls ludwig
branches  tags      trunk
\end{lstlisting}
which is the usual svn convention for trunk, branches and tags.
The process for committing code is described in section \ref{xref:developers}.

If you look in  the \texttt{trunk} directory, you should see
\begin{lstlisting}
$ ls trunk
config  LICENSE      mpi_s   src       tests  version.h
docs    Makefile.mk  README  targetDP  util
\end{lstlisting}

@@

Output for colloidal particle data is again to file with a name encoding
the time step and parallel decomposition of the output. For example,
\begin{lstlisting}
bash-3.2$ ls config*
config.cds00000020.001-001
\end{lstlisting}
contains particle data for time step 20 in a format described in
Section~\ref{examples}.
These data may be requested in ASCII or raw binary format.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  intro.tex
%
%  Contains introduction and quick start for users.
%
%  Edinburgh Soft Matter and Statistical Physics Group and
%  Edinburgh Parallel Computing Centre
%
%  (c) 2016-2018 The University of Edinburgh
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The code is publicly available from
\texttt{http://github/ludwig-cf/ludwig/}
which provides revision control via git, issue tracking, and so on.

The current stable release is available as the master branch.

@@

Output for colloidal particle data is again to file with a name encoding
the time step and parallel decomposition of the output. For example,
\begin{lstlisting}
bash-3.2$ ls config*
config.cds00000020.001-001
\end{lstlisting}
contains particle data for time step 20 in a format described in
Section~\ref{section-examples}.
These data may be requested in ASCII or raw binary format.
